---
title: "OS FFPE pathwest Salmon data"
author: "Sulev Koks"
date: "04/01/2024"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries and data file

```{r}
library(tximeta)
library(DESeq2)
```

```{r}
load("DDSgseFFPEOSsalmon.RData")
```

```{r}
dds <- DESeq(ddsgse)
```

```{r}
(res <- results(dds,  alpha=0.05))
summary(res)
resOrdered <- res[order(res$padj),]
head(resOrdered)
```

Very good and easy annotation with `AnnotationDbi`

```{r}
library("AnnotationDbi")
library("org.Hs.eg.db")
```

This is the organism annotation package ("org") for *Homo sapiens* ("Hs"), organised as an *AnnotationDbi* database package ("db"), using Entrez Gene IDs ("eg") as primary key.
To get a list of all available key types, use:

```{r adjust rownames}
row.names(res)[1:10]
res$TX<-row.names(res)
rownames(res)<- gsub("\\..*", "", res$TX)
rownames(res)[1:10]
columns(org.Hs.eg.db)
```

We can use the *mapIds* function to add invidual columns to our results table. To add the gene symbol and Entrez ID, we call *mapIds* twice:

```{r annot}
res$genename <- mapIds(org.Hs.eg.db, 
                     keys=row.names(res), 
                     column="GENENAME", 
                     keytype="ENSEMBL",
                     multiVals="first")
res$symbol <- mapIds(org.Hs.eg.db, 
                     keys=row.names(res), 
                     column="SYMBOL", 
                     keytype="ENSEMBL",
                     multiVals="first")
res$entrez <- mapIds(org.Hs.eg.db, 
                     keys=row.names(res), 
                     column="ENTREZID", 
                     keytype="ENSEMBL",
                     multiVals="first")
res$omim <- mapIds(org.Hs.eg.db, 
                     keys=row.names(res), 
                     column="OMIM", 
                     keytype="ENSEMBL",
                     multiVals="first")
res$map <- mapIds(org.Hs.eg.db, 
                     keys=row.names(res), 
                     column="MAP", 
                     keytype="ENSEMBL",
                     multiVals="first")
```

Now the results have the desired external gene ids.

```{r}
resOrdered <- res[order(res$padj),]
head(resOrdered)
```

```{r}
sessionInfo()
```


