---
title: "Venn Diagram, Osteosarcoma FFPE Pathwest"
author: "Sulev Koks"
date: "09/01/2024"
output: html_document
editor_options: 
  chunk_output_type: console
---

My samples have these numbers of DEGs:

FRESH = sample(genes,5366), 
FFPEVNEE = sample(genes,17562), 
FFPEPW1 = sample(genes,1701),
FFPEPW2 = sample(genes,10100)

```{r}
library(VennDiagram)
library(ggplot2)
myCol <- c("#F8766D", "#00BFC4", "#7CAE00", "#EFC000FF")
myFill <- c(alpha("#F8766D",0.3), alpha("#00BFC4",0.3), alpha("#7CAE00",0.3), alpha("#EFC000FF",0.3))
```

######
Here we will use `nVennR` package
Original list of genes is needed as the package will perform a comparison of the gene symbols.

```{r}
#devtools::install_github("vqf/nVennR")
```
```{r}
#install.packages("grImport2")
```

```{r}
library(nVennR)
library(grImport2)
```

My samples are in four files

```{r}
load("~/Documents/R_Data/OSPathWest/fresh.RData")
load("~/Documents/R_Data/OSPathWest/ffpevnee.RData")
load("~/Documents/R_Data/OSPathWest/ffpePW1.RData")
load("~/Documents/R_Data/OSPathWest/ffpePW2.RData")
```

This helps to get one version of the Venn diagram.

```{r}
myV <- plotVenn(list(Fresh=fresh, FFPEVNEE=ffpevnee, FFPEPW1=ffpePW1, FFPEPW2=ffpePW2), sNames=c("Fresh", "FFPEvnee", "FFPEpw1", "FFPEpw2"))
```

Make a .svg file.

```{r}
myV <- plotVenn(nVennObj = myV,  outFile="VennOS.svg")
```

```{r}
dev.off()
```

Here we try `VennDiagram` package

```{r}
lists <- list(fresh, ffpevnee, ffpePW1, ffpePW2)
overlap <- calculate.overlap(lists)
overlap_values <- lapply(overlap, function(x) length(x))
```

This is a very nice VENN diagram based on the four lists of OS FFPE genes.

```{r}
draw.quad.venn(area.vector = c(overlap_values$a1, overlap_values$a2, overlap_values$a3, overlap_values$a4, overlap_values$a5, overlap_values$a6, overlap_values$a7, overlap_values$a8, overlap_values$a9, overlap_values$a10, overlap_values$a11, overlap_values$a12, overlap_values$a13, overlap_values$a14, overlap_values$a15), direct.area = T, category = c("FRESH","FFPEVNEE", "FFPEPW1", "FFPEPW2"), 
    scaled=TRUE, main="Osteosarcoma meta-analysis",
    lwd = 2, col = myCol, cex = 1.5,fontfamily = "sans",
    cat.cex = 1.5, cat.fontface = "bold", 
    cat.default.pos = "outer", cat.fontfamily = "sans",
    fill = myFill)
```

```{r}
dev.off()
```

```{r}
sessionInfo()
```